Allocate landings to Georges Bank EPU

### 2020-12-02 docs/allocateLandingsEPU.Rmd
add citations to allocateLandingsEPU.rmd

---
title: "Allocate landings to Georges Bank EPU"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
options(warn=-1)
```

@@

```{r GBfoot, echo=F, eval=T}
crs <- 4326
# NEW GB EPU def based on survey strata
coast <- sf::st_read(here::here("gis", 'NES_LME_coast.shp'), quiet = T) %>%
  sf::st_transform(.,crs=crs)
GB_strata <- sf::st_read(here::here("gis","GB_SOE_strata.shp"),quiet=T) %>%
    sf::st_transform(.,crs=crs)

@@

```{r GBfootstat,echo=F, eval=T}
crs <- 4326
# read in coastline and GB shape file
coast <- sf::st_read(here::here("gis", 'NES_LME_coast.shp'), quiet = T) %>%
  sf::st_transform(.,crs=crs)
GB_strata <- sf::st_read(here::here("gis","GB_SOE_strata_stat.shp"),quiet=T) %>%
    sf::st_transform(.,crs=crs)

@@

## Method for partioning catch data

VTR data is used ... (DePiper, 20xx) and combined with DMIS data. (Need to expand on this). These methods are available within the [`offshoreWind`](https://github.com/dcorvi/offshoreWind) R package. It is necessary to run the package from the server (the `mars` server is recommended).

@@

```{r calc_props_sp, echo = F, eval=T, out.width="100%"}
source(here::here("data-raw","plot_landings_proportions.r"))
plot_landings_proportions(species="cols")

@@

The same data is represented in the plot below but the species are plotted as rows instead of columns
```{r calc_props_st, echo = F, eval=T, out.width="100%"}
plot_landings_proportions(species="rows")

@@

```{r calc_lands, echo = F, eval=T, out.width="100%"}
source(here::here("data-raw","plot_landings.r"))
plot_landings()

@@

>>>>

---
title: "Allocate landings to Georges Bank EPU"
author: Andy Beet
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_fold: hide
csl: apa-annotated-bibliography.csl
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      warning = FALSE)
library(magrittr)
options(warn=-1)
```

@@

```{r GBfoot, eval=T}
crs <- 4326
# NEW GB EPU def based on survey strata
coast <- sf::st_read(here::here("gis", 'NES_LME_coast.shp'), quiet = T) %>%
  sf::st_transform(.,crs=crs)
GB_strata <- sf::st_read(here::here("gis","GB_SOE_strata.shp"),quiet=T) %>%
    sf::st_transform(.,crs=crs)

@@

```{r GBfootstat, eval=T}
crs <- 4326
# read in coastline and GB shape file
coast <- sf::st_read(here::here("gis", 'NES_LME_coast.shp'), quiet = T) %>%
  sf::st_transform(.,crs=crs)
GB_strata <- sf::st_read(here::here("gis","GB_SOE_strata_stat.shp"),quiet=T) %>%
    sf::st_transform(.,crs=crs)

@@

## Method for partitioning catch data

```{r vtrdmisdata, eval=T}
data <- readRDS(here::here("data-raw","Landings_VTR_Geret_Data_summarized.rds"))
yearRange <- data %>% dplyr::distinct(YEAR) %>% range
```

Methods found in [@depiper2014; & @benjamins2018] are implemented in the [`offshoreWind`](https://github.com/dcorvi/offshoreWind) R package. It is necessary to run the package from the server (the `mars` server is recommended).

In summary:

-   VTR data are joined with observer data and a model is specified ( @depiper2014) to assign ...

-   Raster files are then created for each year

-   expand ..

-   The landings data span the period from `r paste0(yearRange,collapse="-")`.

-   Landings are assigned to each of the statistical areas (`r statAreas`)

-   The landings with each statistical area (for each year) are then allocated to each portion of a statistical area (within Georges Bank and outside Georges Bank)

-   The proportion of landings attributed to Georges Bank are then calculated and displayed below

@@

```{r calc_props_sp, eval=T, out.width="100%"}
source(here::here("data-raw","plot_landings_proportions.r"))
plot_landings_proportions(species="cols")

@@

The same data is represented in the plot below but the species are plotted as rows instead of columns

```{r calc_props_st, eval=T, out.width="100%"}
plot_landings_proportions(species="rows")

@@

```{r calc_lands,  eval=T, out.width="100%"}
source(here::here("data-raw","plot_landings.r"))
plot_landings()

@@

## References
